---
title: "FinalProject"
author: "Pranit Hande(3971628),Pranav Dev(S3974689),Sajeevan Selvaraj (S3975965)"
date: "`r Sys.Date()`"
output: html_document
---

#Importing required libraries
```{r}
rm(list=ls())  # Careful! This clears all of R's memory!
library(ggplot2)
library(ggpubr)
library(ks)
library(rjags)
library(runjags)

```

```{r}
setwd("C:/Users/prani/Desktop/bayesian/Assignment3")
source("DBDA2E-utilities.R")  

```


#Preliminary functions for posterior inferences
```{r}
#===============PRELIMINARY FUNCTIONS FOR POSTERIOR INFERENCES====================

# Summary MCMC ####
smryMCMC_HD = function(  codaSamples , compVal = NULL,  saveName=NULL) {
  summaryInfo = NULL
  mcmcMat = as.matrix(codaSamples, chains=TRUE)
  paramName = colnames(mcmcMat)
  for ( pName in paramName ) {
    if (pName %in% colnames(compVal)){
      if (!is.na(compVal[pName])) {
        summaryInfo = rbind( summaryInfo, summarizePost( paramSampleVec = mcmcMat[,pName], compVal = as.numeric(compVal[pName]) ))
      }
      else {
        summaryInfo = rbind( summaryInfo, summarizePost( paramSampleVec = mcmcMat[,pName] ) )
      }
    } else {
      summaryInfo = rbind( summaryInfo, summarizePost( paramSampleVec = mcmcMat[,pName] ) )
    }
  }
  rownames(summaryInfo) = paramName
  if ( !is.null(saveName) ) {
    write.csv( summaryInfo , file=paste(saveName,"SummaryInfo.csv",sep="") )
  }
  return( summaryInfo )
}
#################################################################################
# Function to plot MCMC #

# Function to plot MCMC
plotMCMC = function( codaSamples , data , xName="x" , yName="y" ,
                     showCurve=FALSE ,  pairsPlot=FALSE ,
                     saveName=NULL , saveType="jpg" ) {
  #-----------------------------------------------------------------------------
  y = data[,yName]
  x = as.matrix(data[,xName])
  mcmcMat = as.matrix(codaSamples, chains=TRUE)
  chainLength = NROW( mcmcMat )

  # Using correct parameter names from codaSamples
  beta0 = mcmcMat[,"beta0"]
  beta  = mcmcMat[,grep("^beta\\[",colnames(mcmcMat))]
  if ( ncol(x)==1 ) { beta = matrix( beta , ncol=1 ) }

  tau = mcmcMat[,"tau"] 
  zVar = mcmcMat[,"zVar"] 

  # Predictions
  pred1 = mcmcMat[,"pred[1]"]
  pred2 = mcmcMat[,"pred[2]"]
  pred3 = mcmcMat[,"pred[3]"]
  pred4 = mcmcMat[,"pred[4]"]
  pred5 = mcmcMat[,"pred[5]"]

  #-----------------------------------------------------------------------------
  # Compute R^2 for credible parameters:
  YcorX = cor( y , x ) # correlation of y with each x predictor
  Rsq = beta %*% matrix( YcorX , ncol=1 )
  Rsq = Rsq[,1]
  #-----------------------------------------------------------------------------
  if ( pairsPlot ) {
    # Plot the parameters pairwise, to see correlations:
    openGraph()
    nPtToPlot = 1000
    plotIdx = floor(seq(1,chainLength, by=chainLength/nPtToPlot))
    panel.cor = function(x, y, digits=2, prefix="", cex.cor, ...) {
      usr = par("usr"); on.exit(par(usr))
      par(usr = c(0, 1, 0, 1))
      r = (cor(x, y))
      txt = format(c(r, 0.123456789), digits=digits)[1]
      txt = paste(prefix, txt, sep="")
      if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
      text(0.5, 0.5, txt, cex=1.25)
    }
    pairs( cbind( beta0, beta, tau )[plotIdx,],
           labels=c( "beta[0]", paste0("beta[",1:ncol(beta),"]\n",xName), 
                     expression(tau) ), 
           lower.panel=panel.cor, 
           col="skyblue" )
    if ( !is.null(saveName) ) {
      saveGraph( file=paste(saveName,"PostPairs",sep=""), type=saveType)
    }
  }
  #-----------------------------------------------------------------------------
  # Marginal histograms:
  
  decideOpenGraph = function( panelCount , saveName , finished=FALSE , 
                              nRow=2 , nCol=3 ) {
    if ( finished==TRUE ) {
      if ( !is.null(saveName) ) {
        saveGraph( file=paste0(saveName,ceiling((panelCount-1)/(nRow*nCol))), 
                   type=saveType)
      }
      panelCount = 1 
      return(panelCount)
    } else {
      if ( ( panelCount %% (nRow*nCol) ) == 1 ) {
        if ( panelCount>1 & !is.null(saveName) ) {
          saveGraph( file=paste0(saveName,(panelCount%/%(nRow*nCol))), 
                     type=saveType)
        }
        openGraph(width=nCol*7.0/3,height=nRow*2.0)
        layout( matrix( 1:(nRow*nCol) , nrow=nRow, byrow=TRUE ) )
        par( mar=c(4,4,2.5,0.5) , mgp=c(2.5,0.7,0) )
      }
      panelCount = panelCount+1
      return(panelCount)
    }
  }

  # Original scale:
  panelCount = 1
  panelCount = decideOpenGraph( panelCount , saveName=paste0(saveName,"PostMarg") )
  histInfo = plotPost( beta0, cex.lab=1.75, showCurve=showCurve, xlab=bquote(beta[0]), main="Intercept" )
  for ( bIdx in 1:ncol(beta) ) {
    panelCount = decideOpenGraph( panelCount , saveName=paste0(saveName,"PostMarg") )
    histInfo = plotPost( beta[,bIdx], cex.lab=1.75, showCurve=showCurve, xlab=bquote(beta[.(bIdx)]) , main=xName[bIdx] )
  }

  panelCount = decideOpenGraph( panelCount, finished=TRUE, saveName=paste0(saveName, "PostMarg") )
  
  # tau
  panelCount = decideOpenGraph( panelCount, saveName=paste0(saveName,"PostMarg2") )
  histInfo = plotPost( tau, cex.lab=1.75, showCurve=showCurve, xlab=bquote(tau), main=paste("Scale") )
  
  # R-squared
  panelCount = decideOpenGraph( panelCount, saveName=paste0(saveName,"PostMarg2") )
  histInfo = plotPost( Rsq, cex.lab=1.75, showCurve=showCurve, xlab=bquote(R^2), main=paste("Prop Var Accntd") )
  
  # Predictions
  panelCount = decideOpenGraph( panelCount, saveName=paste0(saveName,"PostMargPred") )
  histInfo = plotPost( pred1, cex.lab=1.75, showCurve=showCurve, xlab="Prediction 1", main="Case 1 predicted \ninsurance charge" )
  panelCount = decideOpenGraph( panelCount, saveName=paste0(saveName, "PostMargPred") )
  histInfo = plotPost( pred2, cex.lab=1.75, showCurve=showCurve, xlab="Prediction 2", main="Case 2 predicted \ninsurance charge" )
  panelCount = decideOpenGraph( panelCount, saveName=paste0(saveName, "PostMargPred") )
  histInfo = plotPost( pred3, cex.lab=1.75, showCurve=showCurve, xlab="Prediction 3", main="Case 3 predicted \ninsurance charge" )
  panelCount = decideOpenGraph( panelCount, saveName=paste0(saveName, "PostMargPred") )
  histInfo = plotPost( pred4, cex.lab=1.75, showCurve=showCurve, xlab="Prediction 4", main="Case 4 predicted \ninsurance charge" )
  panelCount = decideOpenGraph( panelCount, saveName=paste0(saveName, "PostMargPred") )
  histInfo = plotPost( pred5, cex.lab=1.75, showCurve=showCurve, xlab="Prediction 5", main="Case 5 predicted \ninsurance charge" )

  panelCount = decideOpenGraph( panelCount, finished=TRUE, saveName=paste0(saveName, "PostMargPred") )
  
  # Standardized scale:
  panelCount = 1
  panelCount = decideOpenGraph( panelCount , saveName=paste0(saveName,"PostMargZ") )
  histInfo = plotPost( beta0 , cex.lab = 1.75 , showCurve=showCurve ,
                       xlab=bquote(beta[.(bIdx)]) , main="Intercept" )
  for ( bIdx in 1:ncol(beta) ) {
    panelCount = decideOpenGraph( panelCount , saveName=paste0(saveName,"PostMargZ") )
    histInfo = plotPost( beta[,bIdx] , cex.lab = 1.75 , showCurve=showCurve ,
                         xlab=bquote(beta[.(bIdx)]) , main=xName[bIdx] )
  }
  
  panelCount = decideOpenGraph( panelCount, finished=TRUE, saveName=paste0(saveName, "PostMargZ") )
  
  # Scale
  panelCount = decideOpenGraph( panelCount , saveName=paste0(saveName,"PostMargZ2") )
  histInfo = plotPost( zVar, cex.lab=1.75, showCurve=showCurve, xlab=bquote(tau), main=paste("Scale") )
  
  # R-squared
  panelCount = decideOpenGraph( panelCount , saveName=paste0(saveName,"PostMargZ2") )
  histInfo = plotPost( Rsq , cex.lab = 1.75 , showCurve=showCurve ,
                       xlab=bquote(R^2) , main=paste("Prop Var Accntd") )
  panelCount = decideOpenGraph( panelCount , finished=TRUE , saveName=paste0(saveName,"PostMargZ2") )
}

```

# Reading the data
```{r}
charges <- read.csv("expenses.csv")
head(charges)

```


#Label encoding 
```{r}
charges$sex <- ifelse(charges$sex == "male", 1, 0) # Encoding 'sex' column (Male = 1, Female = 0)
charges$smoker <- ifelse(charges$smoker == "yes", 1, 0) #Encoding 'smoker' column (Yes = 1, No = 0)
charges$region <- as.numeric(factor(charges$region))#Convert 'region' to factor and then to numeric (northeast = 1 ,northwest = 2, southeast = 3, southwest = 4)
head(charges, n = 10)
```

# Summary statistics
```{r}
summary(charges)
```

#Data Visualization
```{r}
#Scatter plot of Charges vs Age
p1 <- ggplot(charges, aes(x = age, y = Y)) +
  geom_point(color = "#01579B") +
  labs(title = "Scatterplot of Charges vs Age", x = "Age", y = "Charges")+ 
  ggtitle("Figure 4.1 Scatter plot of Charges vs Age")

#Scatterplot of Charges vs BMI
p2 <- ggplot(charges, aes(x = bmi, y = Y)) +
  geom_point() +
  labs(title = "Charges vs BMI", x = "BMI", y = "Charges")

# Display plots side by side
ggarrange(p1 , p2, nrow = 1, ncol = 2)
```

#Additional plots for data exploration
```{r}
#Color palette for the following graph
color_palette <- c("Female" = "#A6CEE3", "Male" = "#1F78B4", 
                   "No" = "#A6CEE3", "Yes" = "#1F78B4",
                   "southwest" = "#B3E5FC", "southeast" = "#4FC3F7", 
                   "northwest" = "#0288D1", "northeast" = "#01579B")

# Gender Boxplot
p1 <- ggplot(charges, aes(x = sex, y = Y, fill = sex)) +
  geom_boxplot(alpha = 0.6, outlier.color = "red", outlier.shape = 1) +
  xlab("Gender") + ylab("Charges") +
  scale_fill_manual(values = color_palette[c("Female", "Male")]) +
  ggtitle("Figure 4.2 Box Plot of Insurance Charges by Gender") +
  theme_minimal() + theme(legend.position = "none")

# Smoking Status Boxplot with increased y-axis limit
p2 <- ggplot(charges, aes(x = smoker, y = Y, fill = smoker)) +
  geom_boxplot(alpha = 0.6, outlier.color = "red") +
  scale_fill_manual(values = color_palette[c("No", "Yes")]) +
  labs(x = "Smoker Status", y = "Charges", title = "Figure 4.3 Box Plot of Charges by Smoking Status") +
  ylim(0, 70000) +  # Adjust the upper limit as needed
  theme_minimal() + theme(legend.position = "none")


# Region Boxplot
p3 <- ggplot(charges, aes(x = region, y = Y, fill = region)) +
  geom_boxplot() +
  scale_fill_manual(values = color_palette[c("southwest", "southeast", "northwest", "northeast")]) +
  labs(x = "Region", y = "Charges", title = "Figure 4.4 Box Plot of Charges vs Region") +
  theme_minimal() + theme(legend.position = "none")
  

# BMI Scatter Plot by Gender
p4 <- ggplot(charges, aes(x = bmi, y = Y, color = factor(sex, labels = c("Female", "Male")))) +
  geom_point() + xlab("BMI") + ylab("Charges") +
  scale_color_manual(values = color_palette[c("Female", "Male")]) +
  ggtitle("Figure 4.5 Scatter plot of Insurance Charges and \nBMI by Gender") +
  theme_minimal()

# Children Scatter Plot by Gender
p5 <- ggplot(charges, aes(x = children, y = Y, color = factor(sex, labels = c("Female", "Male")))) +
  geom_point() + xlab("No of Children") + ylab("Charges") +
  scale_color_manual(values = color_palette[c("Female", "Male")]) +
  ggtitle("Figure 4.6 Scatter plot of Insurance Charges and \nNo of Children by Gender") +
  theme_minimal()

figure <- ggarrange(p1, p2, p3, p4 , p5, nrow = 3, ncol = 2)
figure

```

#Histogram of the dependent variable
```{r}
hist(charges$Y)
```

# Kernel density estimation
```{r}
plot(kde(charges$Y), xlab = "Charges")
```

# THE DATA.
```{r}

y = charges[,"Y"]
x = as.matrix(charges[,c("age","sex","bmi","children", "smoker", "region")])

```

#Correlation matrix of predictors
```{r}
cat("\nCORRELATION MATRIX OF PREDICTORS:\n ")
show( round(cor(x),3) )
```

#Prediction Matrix
```{r}
xPred = array(NA, dim = c(5,6))
xPred[1,] = c(35, 0, 28.5, 1, 1, 2)  # age,sex(0 = Female), BMI, children, smoker (1 = Yes), region(2 = northwest)
xPred[2,] = c(42, 0, 31.2, 3, 0, 4)  # age,sex(0 = Female), BMI, children, smoker (0 = No), region(4 = southwest)
xPred[3,] = c(27, 0, 22.9, 0, 1, 1)  # age,sex, BMI(0 = Female), children, smoker (1 = Yes), region(1 = northeast)
xPred[4,] = c(55, 1, 29.7, 2, 0, 3)  # age,sex, BMI(1 = Male), children, smoker (0 = No), region(3 = southeast)
xPred[5,] = c(30, 1, 24.8, 1, 0, 2)  # age,sex, BMI(1 = Male), children, smoker (0 = No), region(2 = northwest)

```

# Specify the data in a list, for later shipment to JAGS:
```{r}
dataList <- list(
  x = x ,
  y = y ,
  xPred = xPred ,
  Nx = dim(x)[2] ,
  Ntotal = dim(x)[1]
)
```

```{r}

# THE MODEL.
modelString = "
  
  # Standardize the data:
  
  data {
  # create variables using y
    ysd <- sd(y)
  #standardizing dependent variable (y)
  for ( i in 1:Ntotal ) {
    zy[i] <- y[i] / ysd
  }
  # create variables using x
  for ( j in 1:Nx ) {
    xsd[j] <- sd(x[,j])
    #standardizing the independent variables (x)
    for ( i in 1:Ntotal ) {
      zx[i,j] <- ( x[i,j] ) / xsd[j] 
          #we will not perform centering as we're using a gamma likelihood.
      }
    }
  }
  
  # Specifying the model using the standardized data:
  model {
    for ( i in 1:Ntotal ) {
      zy[i] ~ dgamma( (mu[i]^2)/zVar, mu[i]/zVar )
      mu[i] <- zbeta0 + sum( zbeta[1:Nx] * zx[i,1:Nx] )
    }
    
    # Priors on standardized scale (using expert knowledge):
    zbeta0 ~ dnorm( 0 , 1/2^2 )                                                           
    zbeta[1] ~ dnorm( (100/10000)/xsd[1] , 1/(1/xsd[1]^2))  # Age: Strong expert knowledge, +100 AUD per year
    zbeta[2] ~ dnorm( 0                   , 1/(100/xsd[2]^2))  # Sex: No expert knowledge
    zbeta[3] ~ dnorm( (50/10000)/xsd[3] , 1/(10/xsd[3]^2))   # BMI: Moderate expert knowledge, +50 AUD per BMI unit
    zbeta[4] ~ dnorm( (1000/10000)/xsd[4]         , 1/(100/xsd[4]^2)) # Children: Weak expert knowledge, +1000 AUD per child
    zbeta[5] ~ dnorm( (15000/10000)/xsd[5], 1/(0.1/xsd[5]^2))  # Smoker: Very strong expert knowledge, +15,000 AUD for smokers
    zbeta[6] ~ dnorm( 0                   , 1/(100/xsd[6]^2))  # Region: Weak expert knowledge
    
    zVar ~ dgamma( 0.01 , 0.01 )

    # Transform back to original scale:
    beta[1:Nx] <- ( zbeta[1:Nx] / xsd[1:Nx] )*ysd
    beta0 <- zbeta0*ysd
    tau <- zVar * (ysd)^2

    # Calculating predictions at every step of the MCMC
    for ( i in 1:5){
      pred[i] <- beta0 + beta[1]*xPred[i,1] + beta[2]*xPred[i,2] + beta[3]*xPred[i,3] 
      + beta[4]*xPred[i,4] + beta[5]*xPred[i,5] 
    }
  }
  
  
  "  # close quote for modelString
# Write out modelString to a text file
writeLines( modelString , con="As3.txt" )
```

#Initializing parameters for JAGS model.


#First Implementation

#Initializing parameters for first implementation
```{r}

parameters <- c("beta0", "beta", "tau", "zVar", "pred")
adaptSteps = 1500  
burnInSteps = 300
nChains = 3 
thinSteps = 7
numSavedSteps = 5000
nIter = ceiling( ( numSavedSteps * thinSteps ) / nChains )

```

#Exceuting the JAGS model for first implementation
```{r}
startTime = proc.time()
# Parallel run
runJagsOut <- run.jags( method="parallel" ,
                        model="As3.txt" ,
                        monitor= c("beta0", "beta", "tau", "zVar", "pred") ,
                        data=dataList ,
                        n.chains=nChains ,
                        adapt=adaptSteps ,
                        burnin=burnInSteps ,
                        sample=numSavedSteps ,
                        thin=thinSteps , summarise=FALSE , plots=FALSE )

stopTime = proc.time()
elapsedTime = stopTime - startTime
show(elapsedTime)

```

#CodaSamples for first implementation
```{r}

codaSamples1 = as.mcmc.list( runJagsOut )
nrow(codaSamples1[[1]])

```

#Plotting the diagnostic plots for first implementation
```{r}
fileNameRoot <- "Run1"
graphFileType <- "jpeg"
parameterNames <- varnames(codaSamples1) # get all parameter names
#
for ( parName in parameterNames ) {
  #diagMCMC comes from source("DBDA2E-utilities.R")
  diagMCMC( codaObject = codaSamples1,
            parName = parName , 
            saveName = fileNameRoot, 
            saveType = graphFileType )
}
graphics.off()

```


#Second Implementation

#Initializing parameters for Second Implementation
```{r}
parameters <- c("beta0", "beta", "tau", "zVar", "pred")
adaptSteps2 = 1500  # Number  of steps to "tune" the samplers
burnInSteps2 = 400
nChains2 = 3 
thinSteps2 = 11 
numSavedSteps2 = 8000
nIter2 = ceiling( ( numSavedSteps2 * thinSteps2 ) / nChains2 )

```


#Exceuting the JAGS model for Second Implementation
```{r}

startTime = proc.time()
# Parallel run
runJagsOut2 <- run.jags( method="parallel" ,
                        model="As3.txt" ,
                        monitor= c("beta0", "beta", "tau", "zVar", "pred") ,
                        data=dataList ,
                        n.chains=nChains2 ,
                        adapt=adaptSteps2 ,
                        burnin=burnInSteps2 ,
                        sample=numSavedSteps2 ,,
                        thin=thinSteps2 , summarise=FALSE , plots=FALSE )

stopTime = proc.time()
elapsedTime = stopTime - startTime
show(elapsedTime)


```

#CodaSamples for second implementation
```{r}

codaSamples2 = as.mcmc.list( runJagsOut2 )
nrow(codaSamples2[[1]])

```

#Plotting the diagnostic plots for second implementation
```{r}
fileNameRoot <- "Run2"
graphFileType <- "jpeg"
parameterNames <- varnames(codaSamples2) # get all parameter names
#
for ( parName in parameterNames ) {
  #diagMCMC comes from source("DBDA2E-utilities.R")
  diagMCMC( codaObject = codaSamples2,
            parName = parName , 
            saveName = fileNameRoot, 
            saveType = graphFileType )
}
graphics.off()
```


#Third Implementation

#Initialising the parameters for third Implementation
```{r}

parameters <- c("beta0", "beta", "tau", "zVar", "pred")
adaptSteps3 = 1500  # Number  of steps to "tune" the samplers
burnInSteps3 = 500
nChains3 = 3 
thinSteps3 = 16 
numSavedSteps3 = 9000
nIter3 = ceiling( ( numSavedSteps3 * thinSteps3 ) / nChains3 )


```

#Exceuting the JAGS model for third implementation
```{r}
startTime = proc.time()
# Parallel run
runJagsOut3 <- run.jags( method="parallel" ,
                        model="As3.txt" ,
                        monitor= c("beta0", "beta", "tau", "zVar", "pred") ,
                        data=dataList ,
                        n.chains=nChains3 ,
                        adapt=adaptSteps3 ,
                        burnin=burnInSteps3 ,
                        sample=numSavedSteps3 ,,
                        inits=NULL ,
                        thin=thinSteps3 , summarise=FALSE , plots=FALSE )

stopTime = proc.time()
elapsedTime = stopTime - startTime
show(elapsedTime)
```

#CodaSamples for third implementation
```{r}

codaSamples3 = as.mcmc.list( runJagsOut3 )
nrow(codaSamples3[[1]])

```

#Plotting the diagnostic plots for third implementation
```{r}
fileNameRoot <- "Run3"
graphFileType <- "jpeg"
parameterNames <- varnames(codaSamples3) # get all parameter names
#
for ( parName in parameterNames ) {
  #diagMCMC comes from source("DBDA2E-utilities.R")
  diagMCMC( codaObject = codaSamples3,
            parName = parName , 
            saveName = fileNameRoot, 
            saveType = graphFileType )
}
graphics.off()
```


#Fourth(FINAL) Implementation

#Initialising the parameters for fourth implementation
```{r}

parameters <- c("beta0", "beta", "tau", "zVar", "pred")
adaptSteps4 = 1500  # Number  of steps to "tune" the samplers
burnInSteps4 = 500
nChains4 = 3 
thinSteps4 = 21 
numSavedSteps4 = 10000
nIter4 = ceiling( ( numSavedSteps4 * thinSteps4 ) / nChains4 )


```

#Exceuting the JAGS model for fourth implementation
```{r}
startTime = proc.time()
# Parallel run
runJagsOut4 <- run.jags( method="parallel" ,
                        model="As3.txt" ,
                        monitor= c("beta0", "beta", "tau", "zVar", "pred") ,
                        data=dataList ,
                        n.chains=nChains4 ,
                        adapt=adaptSteps4 ,
                        burnin=burnInSteps4 ,
                        sample=numSavedSteps4 ,,
                        inits=NULL ,
                        thin=thinSteps4 , summarise=FALSE , plots=FALSE )

stopTime = proc.time()
elapsedTime = stopTime - startTime
show(elapsedTime)
```

#CodaSamples for fourth implementation
```{r}

codaSamples4 = as.mcmc.list( runJagsOut4 )
nrow(codaSamples4[[1]])

```

#Plotting the diagnostic plots for fourth implementation
```{r}
fileNameRoot <- "Run4"
graphFileType <- "jpeg"
parameterNames <- varnames(codaSamples4) # get all parameter names
#
for ( parName in parameterNames ) {
  #diagMCMC comes from source("DBDA2E-utilities.R")
  diagMCMC( codaObject = codaSamples4,
            parName = parName , 
            saveName = fileNameRoot, 
            saveType = graphFileType )
}
graphics.off()
```

# Posterior distribution
```{r}
compVal <- data.frame("beta0" = NA, 
                      "beta[1]" = NA, #comparison value for Age
                      "beta[2]" = NA, #comparison value for Sex
                      "beta[3]" = NA, #comparison value for BMI
                      "beta[4]" = NA, #comparison value for Children
                      "beta[5]" = NA, #comparison value for Smoking habits
                      "beta[6]" = NA, #comparison value for Region of residence
                      "tau" = NA , 
                      check.names = FALSE)

summaryInfo <- smryMCMC_HD( codaSamples = codaSamples4, 
                            compVal = compVal )
print(summaryInfo)

graphics.off()
```


```{r}
plotMCMC(codaSamples = codaSamples4, 
         data=charges , 
         xName=c("age","sex","bmi","children", "smoker", "region") , 
         yName="Y" , 
         pairsPlot=TRUE , 
         showCurve=FALSE , 
          )

```


#Mode and Variance of model parameters
```{r}
# model coefficients
coefficients <- summaryInfo[2:8,3] #mode of each parameter
coefficients
Variance <- summaryInfo[9,3] #variance
Variance
# Since we imposed the regression model on the mean of the gamma likelihood,
# we use the model (X*beta) to generate the mean of gamma population for each 
# observed x vector. 
```


#Posterior Predictive Check
```{r}

meanGamma <- as.matrix(cbind(rep(1,nrow(x)),  x)) %*% as.vector(coefficients)
# Generate random data from the posterior distribution. Take the 
# reparameterisation back to alpha and beta.
randomData <- rgamma(n= 231, 
                     shape=meanGamma^2/Variance, 
                     rate=meanGamma/Variance)
# Display the density plot of observed data and posterior distribution:
predicted <- data.frame(InsChg = randomData)
observed <- data.frame(InsChg = y)
predicted$type <- "Predicted"
observed$type <- "Observed"
dataPred <- rbind(predicted, observed)

ggplot(dataPred, aes(InsChg, fill = type)) + geom_density(alpha = 0.2) + xlab("Insurance Charges")

```

